DraftOne

### 2016-06-08 DraftOne.Rmd
Adding outcome data simulation

```{r}
# Function to generate a binary exposure
binary_exposure

binary_exposure(n = 5, p_exp = 0.25)
```

@@

```{r}
# Function to generate a continuous exposure
continuous_exposure

continuous_exposure(n = 5, mu = 10, sd = 10)
```

@@

```{r}
# Get Chicago NMMAPS data and use CVD
library(dlnm)
data(chicagoNMMAPS)
chic <- chicagoNMMAPS
names(chic)
cvd <- chic$cvd

```

@@

### Expected mean baseline for outcome data

@@

```{r}
sim_data <- function(n, rr, x_type = "binary", baseline = "constant",
                     start.date = "2000-01-01", ...){

        require(dplyr)

        if(x_type == "binary"){
                x <- binary_exposure(n = n, ...)
        } else if(x_type == "continuous"){
                x <- continuous_exposure(n = n, ...)
        }

        if(baseline == "constant"){
                exp_base_y <- constant_baseline(n = n, ...)
        }

>>>>

```{r}
# Function to generate a binary exposure
binary_exposure 
binary_exposure(n = 5, p_exp = 0.25)
```

@@

```{r}
# Function to generate a continuous exposure
continuous_exposure 
continuous_exposure(n = 5, mu = 10, sd = 10)
```

@@

```{r}
# Get Chicago NMMAPS data and use CVD
library(dlnm)
data(chicagoNMMAPS)
chic <- chicagoNMMAPS
names(chic)
cvd <- chic$cvd
```

@@

### Expected values for outcome data

@@

```{r}
sim_data <- function(n, rr, x_type = "binary", trend = "constant",
                     start.date = "2000-01-01", ...){

        require(dplyr)
        t <- calc_t(n, trend)
        if(x_type == "binary" & trend = "constant"){
                x <- binary_exposure(n = n, ...)
                simdata <- data.frame(x, sim_binout(n=n, ...))
        } else if(x_type == "continuous" & trend=="constant"){
                x <- continuous_exposure(n = n, ...)
                simdata <- data.frame(x, sim_contout(n=n, ...))
        } else if(x_type == "binary" & trend != "constant"){
                x <- season_binexp(n = n, ...)
                simdata <- data.frame(x, sim_binout(n=n, ...))
        } else if(x_type == "continuous" & trend != "constant"){
                x <- season_contexp(n = n, ...)
                simdata <- data.frame(x, sim_contout(n=n, ...))
        }

        if(trend == "constant"){
                exp_base_y <- constant_baseline(n = n, ...)
        }
